\begin{longtable}[]{@{}cl@{}}
\toprule
\endhead
\textbf{Due:} & Thursday, January 21, 2021 (11:59 PM
PST) \\ \addlinespace
\textbf{Points:} & 60 \\ \addlinespace
\textbf{Name:} &
\texttt{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} \\ \addlinespace
\textbf{Homework buddy:} &
\texttt{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} \\ \addlinespace
\bottomrule
\end{longtable}

\begin{itemize}
\tightlist
\item
  You may collaborate on this homework with \textbf{at most} one person,
  an optional ``homework buddy.''
\item
  \textbf{Submission instructions:} All questions are to be written
  (either by hand or typed) \emph{in the provided spaces} and turned in
  as a single PDF on Gradescope. If you submit handwritten solutions
  write legibly. We reserve the right to give 0 points to answers we
  cannot read. When you submit your answer on Gradescope, \textbf{be
  sure to select which portions of your answer correspond to which
  problem} and clearly mark on the page itself which problem you are
  answering. We reserve the right to give 0 points to submissions that
  fail to do this.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  (3 points) Is this variable declaration OK to do in C++? Why or why
  not?
\end{enumerate}

\begin{verbatim}
double const = 30;
\end{verbatim}

\begin{verbatim}

\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  (4 points) Show 2 different ways to initialize variables in C++.
\end{enumerate}

\begin{verbatim}

\end{verbatim}

\pagebreak

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  (12 points) Mark up this code to show (at least) 4 things that are
  missing.
\end{enumerate}

\begin{verbatim}
#include <iostream>

int main()
    int a(0), b(0), c(0);
    string quote;
    cout << "Enter 3 numbers separated by spaces ";
    cin >> a, b, c;
    sum = a + b + c;
    quote = "The sum of these 3 numbers is "
    cout << quote << sum;
    return 0;
}
\end{verbatim}

\pagebreak

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  (15 points) The program below intends to do the following: Repeatedly
  prompt the user to input an integer number. When the user no longer
  wants to continue, output the sum of all the positive numbers,
  followed by the sum of all the negative numbers. However, the given
  program has errors. Mark all logical and syntax errors in the program
  and provide corrections in the space provided to the right. Add
  missing statements if any.
\end{enumerate}

\begin{verbatim}
#include <iostream>
using namespace std;

int main() {

    int a, sumPositive, sumNegative;

    string promptContinue = "\nTo continue, enter Y/y\n";

    string promptNum = "\nEnter a number: ";

    char response;

    while (reponse = 'y' || 'Y') {

        cout << promptNum;

        cin >> a;

        if (a)
            sumPositive += a;
        else
            sumNegative += a;

        cout << promptContinue;



    }

    cout << "Sum of all positive numbers: " << sumPositive << endl;

    cout << "Sum of all negative numbers: " << sumNegative << endl;

    return 0;
}
\end{verbatim}

\pagebreak

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  (4 points) What is the resulting output from the following C++
  statements? Explain why.
\end{enumerate}

\begin{verbatim}
int x(35), y(5);
bool v, w;
v = (x < y * y);
w = ((x/y) == 7);
cout << (v && w) << endl;
\end{verbatim}

\begin{verbatim}




\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\tightlist
\item
  (6 points) Write code with \textbf{one} \texttt{while} loop that
  prints out these 5 lines like this (remember a newline after each
  line):
\end{enumerate}

\begin{verbatim}
COUNTDOWN TO ZERO: 4
COUNTDOWN TO ZERO: 3
COUNTDOWN TO ZERO: 2
COUNTDOWN TO ZERO: 1
COUNTDOWN TO ZERO: LIFT OFF!
\end{verbatim}

\begin{verbatim}










\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{6}
\tightlist
\item
  (4 points) What is the exact output of the following statements?
\end{enumerate}

\begin{verbatim}
int s = 1;
do {
    cout << s << "+";
}
while (s++ < 5);
\end{verbatim}

\begin{verbatim}

\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{7}
\tightlist
\item
  (4 points) Same question as (7.) but the last statement now reads:
\end{enumerate}

\begin{verbatim}
while (++s <= 5);
\end{verbatim}

\begin{verbatim}

\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{8}
\tightlist
\item
  (4 points) Explain via an example what a ``type mismatch'' is. Also,
  explain how compilers handle C++ statements that have a type mismatch.
\end{enumerate}

\begin{verbatim}







\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{9}
\tightlist
\item
  (4 points) Write an if-else statement that outputs the string ``Grade
  is B'' if the variable \texttt{score} is between 80 and 90 (both
  limits included). Otherwise, the if-else statement should output
  ``Grade is not B''.
\end{enumerate}

\begin{verbatim}


\end{verbatim}
